PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
finished editing ramp employment chunk

## Highest education (baseline, GLAD, EDGI, NBR, RAMP)
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education baseline}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.phd_numeric == "1" ~ 4,
        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        employment.cses_or_equivalent_numeric == "1" ~ 1
      )
    )

@@

>>>>

## Highest education (baseline, GLAD, EDGI, NBR)
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education baseline}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.phd_numeric == "1" ~ 4,
        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        employment.cses_or_equivalent_numeric == "1" ~ 1
      )
    )

@@

## Highest education (baseline, RAMP)
```{r highest level of education for ramp}
if(RAMP == TRUE) {
#create numeric version of the highest education variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        employment.what_is_your_highest_level_of_education == "PhD" ~ 4,
        employment.what_is_your_highest_level_of_education == "Postgraduate degree or equivalent" ~ 4,
        employment.what_is_your_highest_level_of_education == "Master's degree or equivalent" ~ 4,
        employment.what_is_your_highest_level_of_education == "Bachelor's degree or equivalent" ~ 4,
        employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
      )
    )

#recode the numeric version into a factor
employment.raw.id <- employment.raw.id %>%
  mutate(
    highest_education =
      recode_factor(
        highest_education_numeric,
        `1` = "None",
        `2` = "GCSE/CSE",
        `3` = "A-levels",
        `4` = "University")
    )

Check highest education coding for RAMP
```{r Highest education check for RAMP}
if(RAMP == TRUE) {
employment.raw.id %>%
  select(highest_education,
         employment.what_is_your_highest_level_of_education,
         employment.what_is_your_highest_level_of_education_numeric
  )
}
```
